HO unification from object language to meta language

### 2024-04-03 paper/main.tex
typo

In this example, $\hoUnifPb_1$ assigns $A$ which triggers $\linkStore_3$ and
then $\linkStore_4$ by \cref{def:progressetaleft}. $C_{yx}$ is therefore
assigned to $x$ (the second variable of its scope). We can finally see the
\progressetaright of $\linkStore_1$: its \rhs is now $\lambda y.y$ ($C_{xy}$
gives $y$). Since it is no more in \maybeeta, $\lambda y.y$ is unified with
$E_x$. Moreover, $\linkStore_2$ is also triggered due to
\cref{def:progressetaright}: $\lambda x.(f \appsep (lambda y.y) \appsep x)$ is
$\eta$-reducible to $f \appsep (lambda y.y)$ which is a term not starting with
the \elpiIn{lam} constructor.

>>>>

In this example, $\hoUnifPb_1$ assigns $A$ which triggers $\linkStore_3$ and
then $\linkStore_4$ by \cref{def:progressetaleft}. $C_{yx}$ is therefore
assigned to $x$ (the second variable of its scope). We can finally see the
\progressetaright of $\linkStore_1$: its \rhs is now $\lambda y.y$ ($C_{xy}$
gives $y$). Since it is no more in \maybeeta, $\lambda y.y$ is unified with
$E_x$. Moreover, $\linkStore_2$ is also triggered due to
\cref{def:progressetaright}: $\lambda x.(f \appsep (\lambda y.y) \appsep x)$ is
$\eta$-reducible to $f \appsep (\lambda y.y)$ which is a term not starting with
the \elpiIn{lam} constructor.
